Twisted 11-dimensional supergravity, I

### 2021-09-23 suco.tex
backreaction eqns

Moreover, reducing on a circle aong the directions the M5 branes wrap yields the $SU(4)$ invariant twist of IIA on $\R^2\times \C^4$ with N D4 branes wrapping $\R\times \C^2$. \cite{CLSugra} argue that a magnetic coupling of D4 branes to the $SU(4)$ twist of IIA is given by 
\[
\int _{\R\times \C^2} \div^{-1} \mu \vee \Omega_{\C^4}.
\]

\surya{finish}

@@

Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of IIA on $\R^2\times \C_z\times \C^3$ with N D2 branes wrapping $\R\times \C_z$. As is shown in \cite{CLSugra}, an electric coupling of D2 branes to the $SU(4)$ twist of IIA is given by 
\[
I_{D2}(\gamma) = \int_{\R\times\C_z} \gamma
\] 
where $\gamma$ now denotes the 1-form field of the $SU(4)$ twist of type IIA. It is immediate that the pullback of $I_{M2}$ along the map in the proof of proposition \ref{prop:dimred} recovers $I_{D2}$.

@@

The backreacted geoemtry will be given by a solution to the equations of motion upon deforming the 11d action by the interaction $I_{M2}(\gamma)$.

\begin{lem}
The field 
\[
F = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
\]
satisfies the $\mu$-equation of motion in the presence of a stack of $N$ $M2$ branes sourced by the term $N \Omega^{-1} \delta_{w=0}$:
\[
\dbar F + \div F + \frac12 [F, F] = N \Omega^{-1} \delta_{w=0} 
\]
where we set the field in the component $\gamma \in \Omega^{1,\bu}(\CC^5) \otimes \Omega^\bu(\RR)$ equal to zero. 
\end{lem}

\begin{proof}
The equation $\dbar F = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. 
It is clear that $\div F = 0$ and $[F, F] = 0$ by simple type reasons. 
\end{proof}

>>>>

Moreover, reducing on a circle aong the directions the M5 branes wrap yields the $SU(4)$ invariant twist of IIA on $\R^2\times \C^4$ with N D4 branes wrapping $\R\times \C^2$. \cite{CLSugra} argue that a magnetic coupling of D4 branes to the $SU(4)$ twist of IIA is given by 
\[
I_{D4} = \int _{\R\times \C^2} \div^{-1} \mu \vee \Omega_{\C^4}.
\]

Upon dimensionally reducing the interaction $I_{M5}$ along a direction wrapped by the M5 brane, the term depending on the $\theta$ field of type IIA vanishes for type reasons. The result is exactly $I_{D4}$.

To determine the backreacted geometry, we deform the 11d interaction $S_{BF,\infty} + J$ by $I_{M5}$ and look at the $\gamma$-equation of motion. Varying with respect to $\div^{-1}\mu$ and $\gamma$ respectively yield the equations
\begin{align*}
N \delta_{\C^3_z} &= \left (\dbar + d + \div (\frac{\mu}{1-\nu} \right)\partial\gamma \\
0 &= (\dbar + d)\mu + \partial\gamma\partial\gamma
\end{align*}

\begin{lem}
Any background $(\mu = 0, \nu = 0, \gamma = F_{{\rm AdS_7}\times S^4}, \beta = 0)$ where $F_{{\rm AdS_7}\times S^4}$ is such that
\[
\partial F_{{\rm AdS_7}\times S^4} = \# N \frac{dw_1dw_2}{(w_1^2+w_2^2+t^2)^{5/2}}(td \wbar_1\wbar_2 - \wbar_1dtd\wbar_2 + \wbar_2dtd\wbar_1)
\]
satisfies the above equations of motion.
\end{lem}
\begin{proof}
Since $\nu = \mu = 0$, the first equation tells us that $\partial\gamma$ must be the Bochner kernel representing the residue class on $\R\times\C^2 - \{0\}$. The second equation is satisfied for type reasons.
\end{proof}

@@

Moreover, reducing on a circle transverse to the M2 brane yields the $SU(4)$ twist of IIA on $\R^2\times \C_z\times \C^3$ with N D2 branes wrapping $\R\times \C_z$. As is shown in \cite{CLSugra}, an electric coupling of D2 branes to the $SU(4)$ twist of IIA is given by 
\[
I_{D2}(\gamma) = N \int_{\R\times\C_z} \gamma
\] 
where $\gamma$ now denotes the 1-form field of the $SU(4)$ twist of type IIA. It is immediate that the pullback of $I_{M2}$ along the map in the proof of proposition \ref{prop:dimred} recovers $I_{D2}$.

@@

The backreacted geoemtry will be given by a solution to the equations of motion upon deforming the 11d action by the interaction $I_{M2}(\gamma)$. Varying the deformed action with respect to $\gamma$ and $\beta$ respectively yield the equations of motion

\begin{align*}
N \Omega^{-1} \delta_{w=0}  & = \dbar \mu + \frac12 [\mu, \mu] + \partial\gamma\partial\gamma \\
0 & = \div \mu
\end{align*}

\begin{lem}
The background $(\mu = F_{\rm{AdS}_4 \times S^7}, \nu = 0, \gamma = 0, \beta = 0 )$ where 
\[
 F_{\rm{AdS}_4 \times S^7} = \# N \frac{\sum_{a=1}^4 \wbar_a \d \wbar_1 \cdots \Hat{\d \wbar_a} \cdots \d \wbar_4}{\|w\|^{8}} \partial_z .
\]
satisfies the above equation of motion.
\end{lem}

\begin{proof}
Upon specializing $\gamma = 0$, the last term in the first equation above vanishes. The equation $\dbar F_{\rm{AdS}_4 \times S^7} = N \Omega^{-1} \delta_{w=0}$ characterizes the Bochner--Martinelli kernel representing the residue class on $\CC^4 \, \setminus \, 0$. It is clear that $\div F_{\rm{AdS}_4 \times S^7} = 0$ and $[F_{\rm{AdS}_4 \times S^7}, F_{\rm{AdS}_4 \times S^7}] = 0$ by simple type reasons. 
\end{proof}
